The five pillars of computational reproducibility: Bioinformatics and beyond

### 2023-06-10 manuscript/5pillars.Rmd
Add Nekrutenko paper on reproducibility

Documentation is the glue that binds a data science project together.
The published article is the central artifact that outlines the research project and
links to the supporting materials.
From a reproducibility standpoint, the methods section is the most critical part.
It should be detailed enough so that other researchers can understand and replicate the
experiments/analysis and yield similar results.
Unfortunately, key details in bioinformatics data processing procedures are often omitted which limits
their reproducibility [@Garijo2013-zl; @Simoneau2021-kp].
Commonly missing information includes versions of software and packages as well as any parameter setting
and configuration files.
The "Materials Design Analysis Reporting" (MDAR) checklist for authors has been developed to assist in
comprehensive methodological reporting in the life sciences [@Mellor2022-up], and "Minimum Information
About a Bioinformatics Investigation" guidelines describe good reporting practices for computational
biology research [@Tan2010-is].

>>>>

Documentation is the glue that binds a data science project together.
The published article is the central artifact that outlines the research project and
links to the supporting materials.
From a reproducibility standpoint, the methods section is the most critical part.
It should be detailed enough so that other researchers can understand and replicate the
experiments/analysis and yield similar results.
Unfortunately, key details in bioinformatics data processing procedures are often omitted which limits
their reproducibility [@Nekrutenko2012; @Garijo2013-zl; @Simoneau2021-kp].
Commonly missing information includes versions of software and packages as well as any parameter setting
and configuration files.
The "Materials Design Analysis Reporting" (MDAR) checklist for authors has been developed to assist in
comprehensive methodological reporting in the life sciences [@Mellor2022-up], and "Minimum Information
About a Bioinformatics Investigation" guidelines describe good reporting practices for computational
biology research [@Tan2010-is].
